---
title: "Activity Dashboard"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 5
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse) |> suppressPackageStartupMessages()
library(patchwork)
library(ggtext) |> suppressPackageStartupMessages()
library(scales) |> suppressPackageStartupMessages()
library(extrafont)
library(reactable)
library(reactablefmtr)
```

```{r}
source("C:/Users/AYOMIDE/Documents/R/R_Projects/Hotel_/DB_output.R",
       local = knitr::knit_global())
```

```{r}
htl <- readxl::read_xlsx("~/DataG/Hotel data/HotelCustomersDataset.xlsx")
full_country_name <- read_csv(
  "C:/Users/AYOMIDE/Documents/DataG/country_code.csv")

names_country <- select(htl, Nationality) |>
  left_join(full_country_name, by = c("Nationality" = "ISO3"), keep = TRUE) |>
  select(Nationality, country_name) |>
  deframe()

htl <- htl |>
  janitor::clean_names() |>
  mutate(across(c(lodging_revenue, other_revenue), as.double)) |>
  mutate(age = as.integer(age),
         total_revenue = lodging_revenue + other_revenue,
         total_bookings = bookings_canceled + bookings_no_showed + bookings_checked_in,
         country_IS03 = nationality,
         nationality = names_country) |>
  select(-c(id, name_hash, doc_id_hash)) |>
  filter(days_since_last_stay > 0 & days_since_first_stay > 0)
```

Hotel Performance {data-orientation=rows data-vertical_layout=fill}
================================================================================

Row {data-height="200"}
--------------------------------------------------------------------------------

### Average Lead Time
```{r}
htl |>
  filter(average_lead_time >= 0) |>
  summarise(median = median(average_lead_time)) |>
  pull() |>
  
  valueBox(icon = "fa-clock", color = "#F79256")

```

### Unique Nationality
```{r}
n_distinct(htl$nationality) |>
  
  valueBox(icon = "fa-users", color = "#FBD1A2")
```

### Total Revenue
```{r}
htl |>
  summarise(total = sum(total_revenue)) |>
  pull() |>
  comma() |>
  
  valueBox(icon = "fa-euro-sign", color = "#7DCFB6")
```

### Guest Check-In
```{r}
htl |>
  summarise(total_checked_in = sum(bookings_checked_in)) |>
  mutate(
    percentage = round(total_checked_in / sum(htl$total_bookings)*100, 3)) |>
  pull() |>
  paste0("%") |>
  
  valueBox(icon = "fa-user-check", color = "#00B2CA")
```

### Average Room Night
```{r}
htl |>
  summarise(room_nights = round(mean(room_nights), 2)) |>
  pull() |>
  
  valueBox(icon = "fa-bed", color = "#0F80AA")
```

Row {data-height="800"}
--------------------------------------------------------------------------------

### Source of Revenue
```{r}
source_revenue_doughnut_chart()
```

### Revenue Generated & Market Segment
```{r fig.width=8}
revenue_market_segment()
```





Nationality Summary {data-orientation=columns data-vertical_layout=fill}
================================================================================

Column {data-width=500 .tabset .tabset-fade .no-padding}
--------------------------------------------------------------------------------
### Direct
```{r}
country_distibution_channel_plot("Direct")
```

### Travel Agent
```{r}
country_distibution_channel_plot("Travel Agent/Operator")
```

### Corporate
```{r}
country_distibution_channel_plot("Corporate")
```

### E-Platforms
```{r}
country_distibution_channel_plot("Electronic Distribution")
```


### Median average lead time
```{r}
days_summary(df = htl, 
             days_var = "average_lead_time",
             agg_fun = "median")
```

### Maximum average lead time
```{r}
days_summary(df = htl, 
             days_var = "average_lead_time",
             agg_fun = "maximum")
```


Column {data-width=400}
--------------------------------------------------------------------------------
### Country & Distribution Channel
```{r}
country_distribution_channel_table()
```


### Average Lead Time Of Guest
```{r}
country_average_lead_time_table(df = htl)
```





Distribution Channel {data-orientation=rows data-vertical_layout=fill}
================================================================================

Row {data-height=500 .no-padding}
--------------------------------------------------------------------------------
### Unique Guests
```{r fig.width=12}
unique_guest_distribution_channel()
```

### Guest Check In
```{r fig.width=12}
distribution_channel_checked_in_bookings()
```


Row {data-height=500 .no-padding}
--------------------------------------------------------------------------------
### Canceled Bookings
```{r fig.width=12}
distribution_channel_canceled_bookings()
```

### Rate Of Canceled Bookings
```{r fig.width=12}
distribution_channel_canceled_rates()
```




Guest Activity & Revenue {data-orientation=columns data-vertical_layout=fill}
================================================================================
Column {data-width=500 .no-padding}
--------------------------------------------------------------------------------
### Guest Last Stay In The Hotel
```{r}
month_guest_last_stayed()
```

Column {data-width=480}
--------------------------------------------------------------------------------
### Bookings Summary
```{r}
guest_bookings_summary_since_last_stay()
```

### Revenue Summary
```{r fig.width=12}
revenue_generated()
```




Guest Request {data-orientation=columns data-vertical_layout=fill}
================================================================================
Column {data-width=550 .tabset .tabset-fade .no-padding}
--------------------------------------------------------------------------------
### Floor Level
```{r}
guest_request_revenue(df = htl, 
                      request_type = "floor_level",
                      revenue_type = "total_revenue",
                      agg_fun = "median")
```

### Room Features
```{r}
guest_request_revenue(df = htl, 
                      request_type = "room_features",
                      revenue_type = "total_revenue",
                      agg_fun = "median")
```

### Lodging Environment
```{r}
guest_request_revenue(df = htl, 
                      request_type = "room_environment",
                      revenue_type = "total_revenue",
                      agg_fun = "median")
```



Column {data-width=450 .tabset .tabset-fade .no-padding}
--------------------------------------------------------------------------------
### Floor Level
```{r}
guest_request_revenue(df = htl, 
                      request_type = "floor_level",
                      revenue_type = "lodging_revenue",
                      agg_fun = "median")
```

### Room Features 
```{r}
guest_request_revenue(df = htl, 
                      request_type = "room_features",
                      revenue_type = "lodging_revenue",
                      agg_fun = "median")
```

### Lodging Environment
```{r}
guest_request_revenue(df = htl, 
                      request_type = "room_environment",
                      revenue_type = "lodging_revenue",
                      agg_fun = "median")
```


